### 2021-05-21 LaTeX-ACM/sections/paper.tex
changes from call

\section{Introductory Remarks}
\textblue{add sth about the " traversing data structures with e.g., 100 elements on-chain is not possible." contribution somewhere in the intro or contribution section}
For better or worse, blockchain technologies like Ethereum have dramatically lowered the barrier to entry for developing and deploying financial technology. New tokens have been launched with a few clicks of a user interface, and large investment infrastructures have been developed and deployed with little regulatory oversight. Blockchain exchange services allow order-based trading of digital currencies, tokens, and other digital assets. Such exchanges are key components to blockchain-based economic activity.

@@

While Solidity and its compiled bytecode is like many common programming languages, it also has quirks that require experimentation to best optimize performance (\eg factoring in the gas costs of operations, gas refunds, limits to Solidity's object-oriented design, clearing mappings, \etc). We test five priority queues---the core data structure of the call market---and various options for cleaning up our data once finished with it. The bottom line is that the current benchmark for a \cm-esque design is in the low hundreds of trade executions per block on Ethereum today. This positions \cm as a feasible design for only a narrow set of markets today (low liquidity, small number of traders) which is good news for regulators. However we caution that the technology is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum}. While roll-ups use centralized servers and are not fully on-chain, an architecture where these servers only interface with Ethereum and never interface directly with users is still concerning, as it side-steps the regulatory hook that is present in many other server-augmented trading platforms. \textblue{say sth about implementing and testing the full call market on Arbitrum}

@@

\subsection{Front-running} \label{sec:front}

@@

\cm is designed as a base class that can be extended and customized. Here, we discuss potential modifications \textblue{and provide evaluation}.  
% = = = = = = = = = = = = = = = = = = = = = = = = =  %

@@

\textit{Testing Platforms.} Arbitrum currently operates a test network with a bridge contract on the Ethereum Kovan testnet. To experiment with Arbitrum, we implemented a variant of \cm and run the same experiments that we previously performed on Layer 1 (Ethereum). To call functions on \cm, traders can (i) send transactions directly to the inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called an \textit{Aggregator}) provided by the Arbitrum. These aggregators will group and send all pending transactions together as a single Kovan transaction to the EthBridge contract (and pay the gas).

@@

In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing). Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}). \textblue{On Arbitrum, heaps are 32\% more efficient than non-Heaps for submitting orders and 29\% less efficient for closing}. Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. With Arbitrum roll-ups, 38 pairs costs only 1,544 in L1 gas (a 99.9\% savings). This is effectively the cost of recording the \texttt{closeMarket()} function call in the inbox, which is 103 bytes of calldata. As the number of pairs increases, L1 gas cost is constant. For traders submitting an order, the cost is reduced from  207,932 to 2,005.

>>>>

\section{Introductory Remarks}

For better or worse, blockchain technologies like Ethereum have dramatically lowered the barrier to entry for developing and deploying financial technology. New tokens have been launched with a few clicks of a user interface, and large investment infrastructures have been developed and deployed with little regulatory oversight. Blockchain exchange services allow order-based trading of digital currencies, tokens, and other digital assets. Such exchanges are key components to blockchain-based economic activity.

@@

While Solidity and its compiled bytecode is like many common programming languages, it also has quirks that require experimentation to best optimize performance (\eg factoring in the gas costs of operations, gas refunds, limits to Solidity's object-oriented design, clearing mappings, \etc). We test five priority queues---the core data structure of the call market---and various options for cleaning up our data once finished with it. The bottom line is that the current benchmark for a \cm-esque design is in the low hundreds of trade executions per block on Ethereum today. This positions \cm as a feasible design for only a narrow set of markets today (low liquidity, small number of traders) which is good news for regulators. A broader consequence of our research is that any on-chain application that requires the traversal of hundreds of elements in a data structure in a single transaction is not feasible on Ethereum today.

We also speculate that Ethereum is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum} which reduce gas costs by more than 99.9\% savings. While roll-ups are not fully on-chain and introduce new network participants, the roll-up architecture is still concerning to regulators because the participants (called validators) are not directly reachable by users; they only watch the Ethereum state and interact directly with Ethereum.

@@

\subsection{Front-running Evaluation} \label{sec:front}

@@

\cm is designed as a base class that can be extended and customized. Here, we evaluate potential modifications.
% = = = = = = = = = = = = = = = = = = = = = = = = =  %

@@

\textit{Testing Platforms.} Arbitrum currently operates a test network with a inbox contract on the Ethereum Kovan testnet. To experiment with Arbitrum, we implemented a variant of \cm and run the same experiments that we previously performed on Layer 1 (Ethereum). To call functions on \cm, traders can (i) send transactions directly to the inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called an \textit{Sequencer}) provided by the Arbitrum. The sequencer will group, order,  and send all pending transactions together as a single Kovan transaction to the inbox (and pay the gas).

\cm implements an exchange between ETH and tokens. To use Layer 1 assets on Layer 2, Arbitrum provides two bridge contracts: one for ETH, and one for tokens compliant with ERC-20 or other standard interfaces. Prior to trading, a trader uses the bridge to move their ETH to the same address on Layer 2 and then move the ETH to \cm with a Layer 2 transaction. From the user's perspective, tokens work similarly although the backend details are more complex. Finally, withdrawals work essentially same way in reverse, but are only final on Layer 1 after a dispute challenge period (currently 1 hour).\footnote{Layer 1 users might accept assets before they are finalized if they determine their eventual emergence on Layer 1 is indisputable (\textit{eventual finality}).}

@@

In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing). Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}). On Arbitrum, heaps are 32\% more efficient than non-Heaps for submitting orders and 29\% less efficient for closing. Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. With Arbitrum roll-ups, 38 pairs costs only 1,632 in L1 gas (a 99.9\% savings). This is effectively the cost of recording the \texttt{closeMarket()} function call in the inbox, which is 103 bytes of calldata. As the number of pairs increases, L1 gas cost is constant. For traders submitting an order, the cost is reduced from  207,932 to 2,005.
